\thesistitle

### 2019-07-15 sections/research.tex
Explain it well

>>>>

In line 24-25 of the code fragment, we see a \texttt{MethodDeclaration}. The node corresponding with this MethodDeclaration denotes all tokens found on these two lines, line 24 and 25. Although the statements following this method declaration (those that are part of its body) officially belong to the method declaration, they are not included in its graph node. Because of that, in this example, the \texttt{MethodDeclaration} on line 24-25 will be considered a clone of the \texttt{MethodDeclaration} on line 205 even though their bodies might differ. Even the range (the line and column that this node spans) does not include its child statements and declarations.
